Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-28 WSSSPE3/report/wg_main_legacy_SW.tex
adding brief summary of legacy group, and removing corresponding appendix

\subsection{Topic} \todo{change the title to your topic}

\subsubsection{Why it is important}
\todo{short text here}

\subsubsection{Fit with related activities}
\todo{short text here - can include links/cites}

\subsubsection{Discussion}
\todo{short-ish text here}

\subsubsection{Plans}
\todo{short text here - not bullets}

\subsubsection{Landing Page}
\todo{link to landing page}

>>>>

\subsection{Legacy Software}

This group met only briefly, for one period on the first day.  They discussed that it is difficult to define legacy code because there is so much stigma associated with the term. At some point there will be more difficulty and resources wasted trying to keep legacy software supported, but it will eventually be too expensive compared to how much it would be to just rebuild the software or kill it.   Most of the group members were not able to attend on the second day, and those who were able to attend joined other groups.

%\subsubsection{Why it is important}
%\todo{short text here}
%
%\subsubsection{Fit with related activities}
%\todo{short text here - can include links/cites}
%
%\subsubsection{Discussion}
%\todo{short-ish text here}
%
%\subsubsection{Plans}
%\todo{short text here - not bullets}
%
%\subsubsection{Landing Page}
%\todo{link to landing page}
